Untangling the link between traits, size and growth rate in plants

### 2016-07-29 ms/figure_conceptual.tex
Outline of main structure, embed eqn references in table and figure

@@

\newcommand{\rowlabel}[1]{
  \node at ($(thisrow) + (0.25cm, 0cm)$)[anchor=west, text width=2cm] {
  \footnotesize {\color{orange!50}  #1}};
}

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{$\alpha_y$}{output/con/net_mass_production_dt_yield}{$\times$}
\othercol{3}{$\Bigg({\rm P}$}{output/con/net_mass_production_dt_assimilation}{$-$}
\othercol{4}{${\rm R}$}{output/con/net_mass_production_dt_respiration}{$\Bigg)$}
\othercol{5}{$-{\rm T}$}{output/con/net_mass_production_dt_turnover}{}
\rowlabel{(1)}

\defineRow{1}{thisrow}
\rowtitle{Construction costs}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm t}}}$}{output/con/darea_leaf_dmass_live_darea_leaf_dmass_live}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}M_{{\rm l}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_leaf_darea_leaf}{+}
\othercol{3}{$\frac{{\rm d}M_{\textrm{ss}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_sapwood_darea_leaf}{+}
\othercol{4}{$\frac{{\rm d}M_{{\rm sb}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_bark_darea_leaf}{+}
\othercol{5}{$\frac{{\rm d}M_{{\rm r}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_root_darea_leaf}{$\Bigg)^{-1}$}
 \rowlabel{(2)}
\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm t}}}$}{output/con/area_leaf_dt_darea_leaf_dmass_live}{$\times$}
\othercol{3}{$\frac{{\rm d}M_{{\rm t}}}{{\rm d}B}$}{output/con/area_leaf_dt_fraction_allocation_growth}{$\times$}
\othercol{4}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/area_leaf_dt_net_mass_production_dt}{}
\rowlabel{(3)}

\defineRow{3}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{{\rm d}H}{{\rm d}t}$}{output/con/height_dt_height_dt}{}
\othercol{2}{$\frac{{\rm d}H}{{\rm d}A_{{\rm l}}}$}{output/con/height_dt_dheight_darea_leaf}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_leaf_dt_area_leaf_dt}{}
\rowlabel{(4)}

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/con/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}A_{\textrm{ss}}}{{\rm d}A_{{\rm l}}}$}{output/con/area_stem_dt_darea_sapwood_darea_leaf}{$+$}
\othercol{3}{$\frac{{\rm d}A_{\textrm{sb}}}{{\rm d}A_{{\rm l}}}$}{output/con/area_stem_dt_darea_bark_darea_leaf}{\hspace{-0.3em}$\Bigg)$}
\othercol{4}{\hspace{-0.4em}$\times\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_stem_dt_area_leaf_dt}{$+$}
\othercol{5}{$\frac{{\rm d}A_{{\rm sh}}}{{\rm d}t}$}{output/con/area_stem_dt_area_heartwood_dt}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{{\rm d}D}{{\rm d}t}$}{output/con/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{{\rm d}D}{{\rm d}A_{{\rm st}}}$}{output/con/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/con/diameter_stem_dt_area_stem_dt}{}
\rowlabel{(6)}

>>>>

\usepackage{graphicx}
\graphicspath{{../}}

@@

\newcommand{\rowlabel}[1]{
  \node at ($(thisrow) + (-0.75cm, -0.3cm)$)[anchor=west, text width=2cm] {
  \footnotesize {\color{orange!50}\begin{equation}\label{#1}\end{equation}}};
}

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass production rate}
\firstcol{1}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{$\alpha_y$}{output/con/net_mass_production_dt_yield}{$\times$}
\othercol{3}{$\Bigg({\rm P}$}{output/con/net_mass_production_dt_assimilation}{$-$}
\othercol{4}{${\rm R}$}{output/con/net_mass_production_dt_respiration}{$\Bigg)$}
\othercol{5}{$-{\rm T}$}{output/con/net_mass_production_dt_turnover}{}
\rowlabel{eq:dbdt}

\defineRow{1}{thisrow}
\rowtitle{Leaf deployment per mass}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm t}}}$}{output/con/darea_leaf_dmass_live_darea_leaf_dmass_live}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}M_{{\rm l}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_leaf_darea_leaf}{+}
\othercol{3}{$\frac{{\rm d}M_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_sapwood_darea_leaf}{+}
\othercol{4}{$\frac{{\rm d}M_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_bark_darea_leaf}{+}
\othercol{5}{$\frac{{\rm d}M_{{\rm r}}}{{\rm d}A_{{\rm l}}}$}{output/con/darea_leaf_dmass_live_dmass_root_darea_leaf}{$\Bigg)^{-1}$}
 \rowlabel{eq:daldmt}
\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth rate}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm t}}}$}{output/con/area_leaf_dt_darea_leaf_dmass_live}{$\times$}
\othercol{3}{$\frac{{\rm d}M_{{\rm t}}}{{\rm d}B}$}{output/con/area_leaf_dt_fraction_allocation_growth}{$\times$}
\othercol{4}{$\frac{{\rm d}B}{{\rm d}t}$}{output/con/area_leaf_dt_net_mass_production_dt}{}
\rowlabel{eq:daldt}

\defineRow{3}{thisrow}
\rowtitle{Height growth rate}
\firstcol{1}{$\frac{{\rm d}H}{{\rm d}t}$}{output/con/height_dt_height_dt}{}
\othercol{2}{$\frac{{\rm d}H}{{\rm d}A_{{\rm l}}}$}{output/con/height_dt_dheight_darea_leaf}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_leaf_dt_area_leaf_dt}{}
\rowlabel{eq:dhdt}

\defineRow{4}{thisrow}
\rowtitle{Stem-area growth rate}
\firstcol{1}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/con/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}A_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/con/area_stem_dt_darea_sapwood_darea_leaf}{$+$}
\othercol{3}{$\frac{{\rm d}A_{\textrm{sb}}}{{\rm d}A_{{\rm l}}}$}{output/con/area_stem_dt_darea_bark_darea_leaf}{\hspace{-0.3em}$\Bigg)$}
\othercol{4}{\hspace{-0.4em}$\times\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/con/area_stem_dt_area_leaf_dt}{$+$}
\othercol{5}{$\frac{{\rm d}A_{{\rm h}}}{{\rm d}t}$}{output/con/area_stem_dt_area_heartwood_dt}{}
\rowlabel{eq:dast}

\defineRow{5}{thisrow}
\rowtitle{Stem-diameter growth rate}
\firstcol{1}{$\frac{{\rm d}D}{{\rm d}t}$}{output/con/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{{\rm d}D}{{\rm d}A_{{\rm st}}}$}{output/con/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/con/diameter_stem_dt_area_stem_dt}{}
\rowlabel{eq:dDdt}
